Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features

### 2016-12-12 paper/responseToReviewers.tex

\item \emph{Object-based is inappropriate, This paper introduces: no this paper uses the scattering network to try to tackle a specific sound classification task.}
The title has been changed to remove the "object-based" formulation. The particular approach introduced in the paper is the hierarchical representation of a scene as a partition of its distribution of scattering features. While the scattering transform, which has been introduced by previous works, forms the low-level layer of this representation, the hierarchical structure is novel and we believe generic enough to represent auditory scenes for a variety of information retrieval tasks.

\item \emph{The second paragraph of the abstract is vague.}
This paragraph has been reworded and worked into the rest of the abstract in a more fluid manner.

\item \emph{No novel technique is presented}
Again, the hierarchical representation proposed is novel and we provide adequate evidence, in our opinion, for its power in the proposed similarity retrieval task.

\item \emph{the whole paper architecture is poor}
Without any specific points of criticism, it is hard to address this particular statement. Nonetheless, we have reworked the paper as a whole, trying to clarify the overall message.

@@

\item \emph{all the justifications arise from psychoacoustic, bioacoustic,... when the challenge is to classify ambient non natural stationary sounds. For example the whole Gammatone wavelet justification over Morlet is biased}

\item \emph{the classification accuracy is not suited for comparison since the dimension of the feature vectors are not the same for all the techniques }
While the dimension of the features vectors are different, this does not necessarily have to impact the performance of the classification. For example, if we were classifiying stationary Gaussian signals, a spectral envelope feature, like the MFCCs, would prove to be just as accurate, if not better, than the richer second-order scattering transform. The important relationship to consider is whether the feature transform provides an accurate description of the relevant information content in the signal. In addition, most of our experiments deal with the feature vectors through an RBF kernel, which is equivalent to considering the features embedded in an infinite-dimensional space, so in this sense the original dimensionality of the feature vectors carries less importance.

\item \emph{most importantly the used classifier is not the same (from unsupervised GMM to supervised SVM)}
This is an important point and we have included results for MFCCs using a linear SVM. However, we point out that the GMM is also supervised, although it is trained using a generative objective as opposed to a discriminative one, which is the case for the SVM.

@@

\item \emph{the paper reads like a recipe for the specific task without justifications, insights or proofs of the different given definitions and statements.}

\item \emph{The dataset is not well presented since the classes seem to represent stationary noises such as car/tram/train}
While these scenes definitely have a stationary component, such as for the car, tram, train, metro station, and bus classes. This is not sufficient to classify them, since this stationary signal is very similar for these classes. This is why the cluster-based hierarchical representation that we propose is necessary in that it allows the system to pick out the distinct non-stationary components that discriminate between the classes.

@@

\item \emph{line 60: auditory and modulation filter – nonsense.}

\item \emph{"unsupervised classification" it is clustering then.}

The sentence have been rewritten to be more explicit.

\item \emph{"time-frequency perspective or a machine learning perspective" is it imposed versus learned representation? }
The intention was to situate the feature processing step either as post-processing of the scattering features or as pre-processing for the classifier stage. We have removed it during the revision.

@@

\item \emph{Setting of Q1 shall be motivated.}

\item \emph{Reproducibility:  data sets are publicly available, the author do not mention if they plan to make their model available.}

Experiments have been performed in the Matlab environment using open source libraries an all the authors are committed to comply to the reproducible research statements. Unfortunately, due to time constraints, we will not be able to deliver the code at the time of submission of the revision. Nevertheless, it will be fully available at the time of publication if the revision is accepted for publication.

\item \emph{In the last experience (Table III) GMM(MFCC) may be compared to SVM(MFCC) (in addition to SVM(logscat)). There is somewhere a high dimension effect that shall be clarified.}
We have added results for SVM on MFCCs. As mentioned in the response to the other reviewer, we believe that the high dimensionality should not have a significant effect on these results. \ja{Although perhaps we should indeed talk about this in the paper.}

### 2016-12-13 paper/structureScene.tex
Change kernel K definition per #4

The similarity between the scene centroids $\mu_i$ in the entire dataset, where $i=\lbrace1,2,\ldots,I \rbrace$ for $I=U \times M$, is computed using a radial basis function (RBF) kernel $K$ combined with the local scaling method proposed in \cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K_{ij} = \exp\left( - \dfrac{\Vert \mu_i - \mu_j \Vert^2}{\Vert \mu_i - \mu_{k,i} \Vert \Vert \mu_j - \mu_{k,j} \Vert} \right).
\end{equation} 
Here, $\mu_{k,i}$ and $\mu_{k,j}$ are the $k^{\textrm{th}}$ nearest neighbor to the centroids $\mu_i$ and $\mu_j$, respectively, and $\Vert \cdot \Vert$ denotes the Euclidean norm. \ja{Wouldn't it be clearer to define $K$ using scene indices $u$ and $v$ and feature indices $m$ and $n$?}

To compute the similarity between two scenes, we then consider several centroid-based similarity metrics:
\begin{itemize}
\item \emph{ob-closest} (\emph{ob-c}): the similarity between two scenes is equal to the largest similarity between their centroids,
\item \emph{ob-averaged} (\emph{ob-a}): the similarity between two scenes is equal to the average of their centroid similarities, and
\item \emph{ob-weighted} (\emph{ob-w}): the similarity between two scenes is computed using a variant of the earth mover's distance applied to the set of centroids weighted by the number of frames assigned to its cluster.
\end{itemize}

@@

\begin{equation*}
\sum\limits_{n,m}f_{nm} = \min\left( \sum\limits_{n} w_n^u ,\sum\limits_{m} w_m^v \right)
\end{equation*} 
%\ja{Can we provide some interpretation for the different terms and constraints here?}
where $\lbrace f_{nm} \rbrace$ is the flow between the cluster weights $w_n^u$ and $w_m^v$, that is, the amount transported from the $n^{\textrm{th}}$ bin to ``supply the demand'' of the $m^\textrm{th}$ bin, and $\alpha$ is a parameter which trades off between \ja{?}. We denote by $D^{uv}$ the ground distance, a matrix containing the pairwise distances between the centroids sets $\mu^u$ and $\mu^v$. $D^{uv}$ is computed from the kernel $K$:
\begin{equation*}
D^{uv}=\boldsymbol{1}-K^{(uv)}
\end{equation*}
with $K^{(uv)}$ being the slice of $K$ containing the pairwise similarities between the centroids sets $\mu^u$ and $\mu^v$ of the scenes $s_u$ and $s_v$, respectively. As suggested in \cite{pele2009fast}, we set the tradeoff parameter $\alpha$ to $1$.

>>>>

The similarity between the scene centroids $\mu_m^u$ over the entire dataset, is computed using a radial basis function (RBF) kernel $K$ combined with the local scaling method proposed in \cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K_{mn}^{uv} = \exp\left( - \dfrac{\Vert \mu_m^u - \mu_n^v \Vert^2}{\Vert \mu_m^u - \mu_{m,k}^u \Vert \Vert \mu_n^v - \mu_{n,k}^v \Vert} \right).
\end{equation} 
Here, $\mu_{m,k}^u$ and $\mu_{n,k}^v$ are the $k^{\textrm{th}}$ nearest neighbors to the centroids $\mu_m^u$ and $\mu_n^v$, respectively, and $\Vert \cdot \Vert$ denotes the Euclidean norm.

To compute the similarity between two scenes, we then consider several centroid-based similarity metrics:
\begin{itemize}
\item \emph{ob-closest} (\emph{ob-c}): the similarity between two scenes $s_u$ and $s_v$ is equal to the largest similarity between their centroids, that is
\begin{equation}
	\max_{m,n} K_{mn}^{uv},
\end{equation}
\item \emph{ob-averaged} (\emph{ob-a}): the similarity between two scenes $s_u$ and $s_v$ is equal to the average of their centroid similarities, that is
\begin{equation}
	\frac{1}{M^2} \sum_{m,n} K_{mn}^{uv}
\end{equation}
and,
\item \emph{ob-weighted} (\emph{ob-w}): the similarity between two scenes is computed using a variant of the earth mover's distance applied to the set of centroids weighted by the number of frames assigned to its cluster.
\end{itemize}

@@

\begin{equation*}
\sum\limits_{n,m}f_{nm} = \min\left( \sum\limits_{n} w_n^u ,\sum\limits_{m} w_m^v \right)
\end{equation*} 
%\ja{Can we provide some interpretation for the different terms and constraints here?}
where $\lbrace f_{nm} \rbrace$ is the flow between the cluster weights $w_n^u$ and $w_m^v$, that is, the amount transported from the $n^{\textrm{th}}$ bin to ``supply the demand'' of the $m^\textrm{th}$ bin, and $\alpha$ is a parameter which trades off between \ja{?}. We denote by $D^{uv}$ the ground distance, a matrix containing the pairwise distances between the centroids sets $\mu^u$ and $\mu^v$. $D^{uv}$ is computed from the kernel $K$:
\begin{equation*}
D_{mn}^{uv}=1-K_{mn}^{uv}.
\end{equation*}
As suggested in \cite{pele2009fast}, we set the tradeoff parameter $\alpha$ to $1$.
